The Slowdown of TFP \\ Exogenous and Endogenous Mechanisms

### 2017-12-11 Latex/MacroLunch_Dec2017/macrolunch_dec2017.tex
updated the presentation

\item Another strand of literature: Endogenous TFP with R\&D investment as the key variable
	\begin{itemize}
	\item Comin \& Gertler (2006)
	\item Moran \& Queralto (2017)

@@

Reduced Form
\begin{equation}
\mathbf{X_{t}}
= \underbrace{\mathbf{AD} \mathbf{C(L)}}_\text{$\mathbf{B(L)}$} 
\mathbf{X_{t-1}}
+ \underbrace{\mathbf{AD} \mathbf{_t}}_\text{$\mathbf{i_t}$}
\end{equation}

@@

\begin{equation}
TFP_t =  \underbrace{\varepsilon_t}_\text{surprise tech shock}  + \underbrace{V_{t-k}}_\text{news shock} + \underbrace{IT_{t-k}}_\text{IT shock}  
\end{equation}

@@

	\item Horizon of FEV-maximization: 100 quarters.

@@

%%%%%%% Slide %%%%%%
\begin{frame}
	\frametitle{FEV explained by the two shocks at 40 periods}

@@

>>>>

\item Another strand of literature: Endogenous TFP with R\&D investment as the key variable
	\begin{itemize}
	\item Comin \& Gertler (2006)
	\item Moran \& Queralto (2017)
	\item  Guerron \& Jinnai (2014)

@@

Reduced Form
\begin{equation}
\mathbf{X_{t}}
= \underbrace{\mathbf{AD} \mathbf{C(L)}}_\text{$\mathbf{B(L)}$} 
\mathbf{X_{t-1}}
+ \underbrace{\mathbf{AD} \mathbf{s_t}}_\text{$\mathbf{i_t}$}
\end{equation}

@@

\begin{equation}
TFP_t =   \underbrace{V_{t-k}}_\text{news shock} + \underbrace{IT_{t-k}}_\text{IT shock}  + \underbrace{\varepsilon_t}_\text{surprise tech shock} 
\end{equation}

@@

	\item Horizon of FEV-maximization: 60 quarters.

@@

%%%%%%% Slide %%%%%%
\begin{frame}
	\frametitle{FEV explained by the two shocks at 60 periods}

@@

\vspace{2cm}

For BS, FEV of news was 45\%.
